A mixture of hidden Markov models to predict the lymphatic spread in head and neck cancer

### 2024-01-22 content/manuscript.qmd
add & correct variable access in manuscript

where $T \in \{ \text{early}, \text{advanced} \}$ denotes the T-category. We fix $P_\text{early}(t)$ to a binomial distribution with parameters $n=t_\text{max}=$ {{< var t_max >}} and $p_\text{early}=$ {{< var time-prior.early.p >}}, while the advanced T-category's time-prior is also a binomial distribution where the $p_\text{advanced}$ parameter is learned.

@@

>>>>

where $T \in \{ \text{early}, \text{advanced} \}$ denotes the T-category. We fix $P_\text{early}(t)$ to a binomial distribution with parameters $n=t_\text{max}=$ {{< var model.max_t >}} and $p_\text{early}=$ {{< var model.first_binom_prob >}}, while the advanced T-category's time-prior is also a binomial distribution where the $p_\text{advanced}$ parameter is learned.

@@

In @fig-prevalence-by-subsite, we have plotted the prevalence of involvement in the four LNLs I, II, III, and IV stratified by the primary tumor's subsite. We only included patients with tumors in the gum, floor of mouth, other/unspecified parts of the mouth, palate, oropharynx, tosil, base of tongue, and other/unspecified parts of tongue, resulting in {{< var data.num_patients >}} patients.
